%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Backend Developer} % Job title
    {Thailand Ministry of Health / MUIC (Mahidol University International College)} % Organization
    {Salaya, Thailand} % Location
    {Aug. 2016 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Create and manage the docker deployment of the web application}
        \item {Create basic authentication login, manage user, assign permission}
        \item {Create a system to upload lab data to the system (surveys)}
        \item {Write a micro service api to serve the frontend all of the above system}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Game Developer} % Job title
    {Mahidol University} % Organization
    {Salaya, Thailand} % Location
    {Jan. 2017 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Fuekfon game is a game design for disabled people especially for people that recieve a stroke and lose the ability to move, it is design to be a new kind of rehabilitation program}
        \item {Maintain Fuekfon game this include debugging and adding more feature}
        \item {Add more feature to the game such as adding a timer to all of the game}
        \item {Refactor some of the code to support highscore system for each user}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Developer / Dev Ops} % Job title
    {MUIC / TTET (Toyota Tsusho Electronics Thailand)} % Organization
    {Salaya/Chitlom Bangkok} % Location
    {May 2017 - July 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Phase 1 of TTET traffic incident/parking}
        \item {Write a window segment to slice data for data analysis}
        \item {Write deployment scripts for docker-machine to create aws ec2 instances}
        \item {Deploy and support data science team in running their program on the ec2 instances this include creating a Dockerfile for the data science code}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Engineer / Researcher} % Job title
    {TTET (Toyota Tsusho Electronics Thailand)} % Organization
    {Chitlom, Thailand} % Location
    {Aug. 2017 - Sep. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Benchmark the performance of big table in this case Hbase using geomesa on traffic data}
        \item {Benchmark PostGIS performance on large traffic data}
        \item {Attempt to concurrently read and filter GIS data on PostGIS using scala}
        \item {Make conclusion on the finding on Geomesa and PostGIS performance on TTET traffic data}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Engineer / Dev Ops / Backend Developer} % Job title
    {MUIC / NEXTY (Toyota Tsusho Nexty Electronics Thailand)} % Organization
    {Salaya/Chitlom, Thailand} % Location
    {Jan. 2018 - May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {TTET -> NEXTY Phase 2 for Incident/Parking}
        \item {Write an library to launch jobs on kubernetes}
        \item {Write a data pumper which pump information from the rds into kafka}
        \item {Write a python connector that connect to kafka and pull information to serve the client}
        \item {Deploy web application of the system on docker machine}
        \item {Write a live stream pumper which pump data from kinesis into kafka}
        \item {Write a kafka, redis, kubernetes cleaner to garbage collect existing task}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
